An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-15 paper/paper.tex
Paper: write "The Data Layer" subsection of "Data Exchance" in "BTBackup"

% TODO why do we discuss the different ways to find peers? We only need to talk about predfined hosts

\begin{quote}
\begin{itemize}
\item Local peer discovery. All peers inside local network are discovered by sending broadcast packets. If there are peers with the same secret they respond to the broadcast message and connect.
\item Peer exchange (PEX). When two peers are connected, they exchange information about other peers they know.
\item Known hosts (folder settings). If you have a known host with a static ip:port, you can specify this in Sync client, so that it connects to the peer using this information.
\item DHT. Sync uses DHT to distribute information about itself and obtain the information about other peers with this secret. Sync sends SHA1(Secret):ip:port to DHT to announce itself and will get a list of peers by asking DHT for the following key SHA1(Secret)
\item BitTorrent tracker. BitTorrent Sync can use a specific tracker server to facilitate peer discovery. The tracker server sees the combination of SHA1(secret):ip:port and helps peers connect directly. The BitTorrent Sync tracker also acts like a STUN server and can help do a NAT traversal for peers so that they can establish a direct connection even behind a NAT.
\end{itemize}
\end{quote}

@@

For every file a peer wishes to backup, it must find a predetermined number of nodes that can store the file. To ensure an even distributionof responsibility in the structured overlay network, a random bitstring in the address space of the overlay network is generated. The DHT provides the functionality to find the node whose ID is \texit{closest} to the randomly generated bitstring. The peer then gets the metadata record for the node from the DHT. From the metadata record, the peer can calculate if the node is \textit{obligated} to store its file. We discuss the situation in which a node is obligated to store a peers file in section \ref{sec:Fairness}. The peer also uses the metadata record to ensure the node does not have too many blacklisters. If the node meets both requirements, the peer contacts the node to inform it of the decision. The metadata layer is updated appropriately, and the data layer is used to transfer the file. This process repeats until the predetermined number of nodes are found.

@@

% talking to peers and transferring data
% Synchronization software
% - should auto 
% Use of BitTorrent
%

@@

% Reduction of information leakage

% BTSync crypto and security

>>>>

% TODO why do we discuss the different ways to find peers? We only need to talk about predfined hosts
\begin{quote}
\begin{itemize}
\item Local peer discovery. All peers inside local network are discovered by sending broadcast packets. If there are peers with the same secret they respond to the broadcast message and connect.
\item Peer exchange (PEX). When two peers are connected, they exchange information about other peers they know.
\item Known hosts (folder settings). If you have a known host with a static ip:port, you can specify this in Sync client, so that it connects to the peer using this information.
\item DHT. Sync uses DHT to distribute information about itself and obtain the information about other peers with this secret. Sync sends SHA1(Secret):ip:port to DHT to announce itself and will get a list of peers by asking DHT for the following key SHA1(Secret)
\item BitTorrent tracker. BitTorrent Sync can use a specific tracker server to facilitate peer discovery. The tracker server sees the combination of SHA1(secret):ip:port and helps peers connect directly. The BitTorrent Sync tracker also acts like a STUN server and can help do a NAT traversal for peers so that they can establish a direct connection even behind a NAT.
\end{itemize}
\end{quote}

@@

For every file a peer wishes to backup, it must find a predetermined number of nodes that can store the file. To ensure an even distributionof responsibility in the structured overlay network, a random bitstring in the address space of the overlay network is generated. The DHT provides the functionality to find the node whose ID is \texit{closest} to the randomly generated bitstring. The peer then gets the metadata record for the node from the DHT. From the metadata record, the peer can calculate if the node is \textit{obligated} to store its file. We discuss the situation in which a node is obligated to store a peers file in section \ref{sec:Fairness}. The peer also uses the metadata record to ensure the node does not have too many blacklisters. If the node meets both requirements, the peer uses the data layer to contact the node to inform it of the decision. The metadata layer is updated appropriately, and the data layer is used to transfer the file. This process repeats until the predetermined number of nodes are found.

@@

The data layer is responsible for copying the data to be backed up from the peer to the node. This includes the quick communication by the peer to the node informing it that it is a replicant node for a given file.

Our main contribution in this paper, and the only requirement of the data layer, is that it uses BitTorrent as the data transport portocol. By doing so, we increase the speed of data recovery because the peer can download the data from all replicant nodes simultaneously.

@@

The data that is transported via the data layer is encrypted so that the replicant nodes cannot read it. The strength of the encryption is left unspecified as a means of future-proofing this specification.

% TODO note that this isn't done in the impl
Furthermore, all communication between peers and nodes is encrypted to limit information leakage.
